---
title: "Diagnostic Report -- based on current model outputs (47 countries)"
subtitle: "201910gavi-5 -- central burden estimates"
author: "JHU-Lee Modeling Group"
date: "`r Sys.time()`"
output:
  html_document: default
  pdf_document: default
---



```{r include=FALSE}
### Setup
chooseCRANmirror(ind = 77) #specify the mirror so that the packages can be successfully installed in the non-interactive way
package_list <- c("tidyverse",
                  "knitr",
                  "rstudioapi")
for (package in package_list) {
  if (!require(package = package, character.only = T)) {
    install.packages(pkgs = package, dependencies = TRUE)
    library(package = package, character.only = T)
  }
  library(package = package, character.only = T)
}



current_working_dir <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_working_dir)
campaign_default_output <- list.files('current_outputs/', pattern = "campaign-default.csv$")
no_vaccination_output <- list.files('current_outputs/', pattern = "no-vaccination.csv$")
if (length(campaign_default_output) == 1 & length(no_vaccination_output) == 1) {
  cen_camp  <- read_csv(paste0('current_outputs/', campaign_default_output[1]))
  cen_novax <- read_csv(paste0('current_outputs/', no_vaccination_output[1]))
}else{
  message('There are multiple output files for the scenarios, please delete the duplicates and keep one for each scenario. ')
}

```



## The Model Specs
Specific characteristics of this model are shown in this table. 
```{r include=FALSE}
glimpse(cen_camp)
names(cen_camp)
```


```{r echo=FALSE}

model_spec <- cen_camp %>% 
  mutate(Disease = disease) %>%
  mutate(ModelingGroup = 'JHU-Lee') %>%
  mutate(YearRange = paste0(min(year), '-', max(year))) %>% 
  mutate(AgeRange = paste0(min(age), '-', max(age))) %>% 
  mutate(CountryList = paste(unique(cen_camp$country), collapse = '  -  ')) %>% 
  mutate(SimulatedOutcomes = paste(names(cen_camp)[6:ncol(cen_camp)], collapse='  -  ') ) %>% 
  select(Disease, ModelingGroup, YearRange, AgeRange, CountryList, SimulatedOutcomes) %>% 
  slice(1)

kable(data.frame(Item = names(model_spec), Details = unlist(unname(model_spec[1,]))))

```



## Coverage Trajectories
The trends of the specific coverage sets for the campaign scenario can be observed in this figure. 
```{r include=FALSE}
### get the coverage data from local
cov_novax <- read_csv("data_from_montagu/cov_novax.csv")
cov_camp <- read_csv("data_from_montagu/cov_camp.csv")
  
```


```{r fig.width=10, fig.height=8, echo=FALSE}
### plotting
cov_camp %>%
  filter(country_code %in% unique(cen_camp$country)) %>% 
  ggplot(aes(x=year, y=coverage)) + 
  geom_bar(stat="identity", fill="skyblue", alpha=1.0) + 
  theme_minimal() +
  facet_grid(country_code~.)

```

&nbsp;
Age ranges of the different coverage sets include either standard age ranges (as it is the case of Measles) but sometimes it differs by year and country so that several combinations can be possible (See table below).
```{r echo=FALSE}
### little table
cov_age_df <- cov_camp %>% 
  mutate(coverage_set_name = scenario) %>% 
  mutate(age_from = min(age_first)) %>% 
  mutate(age_to = max(age_last)) %>% 
  mutate(freq = n()) %>% 
  select(coverage_set_name, age_from, age_to, freq) %>% 
  slice(1)

kable(cov_age_df)

```



## Fully vaccinated persons (FVPs)
The estimates of fully vaccinated persons (FVPs) are obtained by multiplying coverage from each coverage set and the target population.
The following picture shows the Fully Vaccinated Persons (FVPs) at global level by scenario for Cholera. 
```{r include=FALSE}
### calculate FVPs
fvps_camp <- cov_camp %>% 
  group_by(year) %>% 
  mutate(GlobalFVPs = sum(target*coverage)) %>% 
  filter(country_code == country_code[1]) %>% 
  select(year, GlobalFVPs) %>% 
  mutate(scenarios = 'Campaign')

fvps_camp <- data.frame(sapply(fvps_camp, rep.int, times=2))
NumRow <- nrow(fvps_camp)

if (length((cov_novax$coverage)) == 0){
  fvps_camp$scenarios[1:NumRow/2] <- 'No Vaccination'
  fvps_camp$GlobalFVPs[1:NumRow/2] <- 0
  fvps_camp$year <- as.numeric(fvps_camp$year)
  fvps_camp$GlobalFVPs <- as.numeric(fvps_camp$GlobalFVPs)
}else{
  message('The no vaccination scenario has non-zero coverage data, please check the coverage dataset from montagu. ')
}


```


```{r echo=FALSE, fig.height=5, fig.width=10}
### Plotting
fvps_camp %>% 
  ggplot(aes(x=year, y=GlobalFVPs/1000000)) + 
  geom_bar(stat="identity", fill="skyblue", alpha=1.0) + 
  theme_minimal() +
  facet_grid(.~scenarios) +
  labs(y = "Fully Vaccinated Persons (in millions)")

```



## Check the general info
Expected number of rows.
```{r echo=FALSE}
outcome_code = rep(names(cen_camp)[6:ncol(cen_camp)], 2)
outcome_num = length(names(cen_camp)[6:ncol(cen_camp)])

kable(data.frame(scenario_description = c(rep('Campaign, Default', outcome_num), rep('No vaccination', outcome_num)),
                 outcome_code = outcome_code,
                 number_of_non_na_rows =  c(colSums(!is.na(cen_camp[outcome_code[1:outcome_num]])),
                                            colSums(!is.na(cen_novax[outcome_code[(outcome_num + 1):(outcome_num*2)]])) )    ))
rm(outcome_code)

```


```{r include=FALSE}
### first merge/join two datasets
stack_camp <- cen_camp %>% mutate(id = paste0(country, as.character(year), as.character(age)))
stack_camp$source <- 'Campaign, Default'
stack_novax <- cen_novax %>% mutate(id = paste0(country, as.character(year), as.character(age)))
stack_novax$source <- 'No vaccination'

stacked <- rbind(stack_novax, stack_camp)
rm(stack_novax)
rm(stack_camp)

### create new variables
num_country <- length(unique(cen_camp$country))

stacked <- stacked %>%
  group_by(year, age, source) %>% 
  mutate( cases1 = case_when(sum(!is.na(cases))< num_country ~ 0,
                             sum(!is.na(cases))==num_country ~ 1) ) %>% 
  mutate( cases2 = sum(cases > 0) ) %>% 
  mutate( cohort_size1 = case_when(sum(!is.na(cohort_size))<num_country ~ 0,
                             sum(!is.na(cohort_size))==num_country ~ 1) ) %>% 
  mutate( cohort_size2 = sum(cohort_size > 0) ) %>%
  mutate( dalys1 = case_when(sum(!is.na(dalys))<num_country ~ 0,
                             sum(!is.na(dalys))==num_country ~ 1) ) %>% 
  mutate( dalys2 = sum(dalys > 0) ) %>%
  mutate( deaths1 = case_when(sum(!is.na(deaths))<num_country ~ 0,
                             sum(!is.na(deaths))==num_country ~ 1) ) %>% 
  mutate( deaths2 = sum(deaths > 0) )

### gather
stacked1 <- stacked %>% 
  gather(new_outcomes, values, c(cases1,cohort_size1,dalys1,deaths1)) 
stacked2 <- stacked %>% 
  gather(new_outcomes, values, c(cases2,cohort_size2,dalys2,deaths2))
rm(stacked)

```


This figure shows the shape of the upload by scenarios and outcomes (whether there are missing values, 1 means no missing value)
```{r echo=FALSE, fig.width=10, fig.height=8}
### plotting
stacked1 %>% 
  ggplot(aes(year, age, fill = values)) + 
  geom_tile() +
  facet_grid(new_outcomes ~ source) +
  scale_fill_gradient(low="steelblue4", high="skyblue") +
  theme_minimal()
rm(stacked1)

```


This figure shows the pattern of positive values (number of positive values across all simulated countries)
```{r echo=FALSE, fig.width=10, fig.height=8}
### another similar plot
stacked2 %>% 
  ggplot(aes(year, age, fill = values)) + 
  geom_tile() +
  facet_grid(new_outcomes ~ source) +
  scale_fill_gradient(low="steelblue4", high="skyblue") +
  theme_minimal()
rm(stacked2)

```



## Check the cohort size
### Notion: the interpolated population dataset doesn't have info for age 100 but has the above, we will leave that out to keep the consistency. 
```{r include=FALSE}
### prepare the datasets
#write.csv(int_pop,"C:/Users/ZOU/Desktop/Diagnostics Report\\montagu_interpolated_pop.csv", row.names = FALSE)
int_pop <- read_csv('data_from_montagu/montagu_interpolated_pop.csv') #this one has all the countries we have to make it smaller
int_pop <- int_pop %>% 
  filter(year >= 2000 & age_to <= 100 & country_code%in%unique(cen_camp$country)) %>% 
  mutate(id = paste0(country_code, as.character(year), as.character(age_to))) %>% 
  select(id, value)
cen_cohort <- cen_camp %>% 
  filter(age < 100) %>% 
  mutate(id = paste0(country, as.character(year), as.character(age)))
pop_plot = full_join(cen_cohort, int_pop, by = 'id')

pop_plot_no_country_class <- pop_plot %>% 
  group_by(age, year) %>% 
  mutate(int_population = sum(value)) %>% 
  mutate(simu_population = sum(cohort_size)) %>% 
  mutate(diff_population = int_population - simu_population) %>% 
  filter(country == unique(cen_camp$country)[1]) %>% 
  gather(population_source, population_value, c(int_population, simu_population, diff_population)) %>% 
  select(-value, -cohort_size, -country)
pop_plot_all_countries <- pop_plot %>% 
  mutate(int_population = value) %>% 
  mutate(simu_population = cohort_size) %>% 
  mutate(diff_population = int_population - simu_population) %>% 
  gather(population_source, population_value, c(int_population, simu_population, diff_population)) %>% 
  select(-value, -cohort_size)
rm(int_pop)
rm(cen_cohort)
rm(pop_plot)

### check if there is NA
sum(is.na(pop_plot_no_country_class[names(pop_plot_no_country_class)[1:ncol(pop_plot_no_country_class)]]))
sum(is.na(pop_plot_all_countries[names(pop_plot_all_countries)[1:ncol(pop_plot_all_countries)]]))

```


This figure shows the comparison of cohort size against interpolated population in all countries. 
```{r echo=FALSE, fig.width=10, fig.height=5}
### plotting
pop_plot_no_country_class %>% 
  ggplot(aes(fill = age, y = population_value/1000000, x = year)) +
  geom_bar(position="stack", stat="identity") +
  scale_fill_distiller(palette = "RdPu") +
  theme_minimal() +
  facet_grid(~factor(population_source, levels=c('int_population','simu_population','diff_population'))) + 
  labs(x = 'calendar year', y = 'people (in millions)')
#rm(pop_plot_no_country_class)

```


This figure shows the comparison of cohort size against interpolated population in the simulated countries. 
```{r echo=FALSE, fig.width=10, fig.height=5}
### plotting
pop_plot_all_countries %>% 
  ggplot(aes(fill = age, y = population_value/1000000, x = year)) +
  geom_bar(position="stack", stat="identity") +
  scale_fill_distiller(palette = "RdPu") +
  theme_minimal() +
  facet_grid(country~factor(population_source, levels=c('int_population','simu_population','diff_population')), scales = 'free') + 
  labs(x = 'calendar year', y = 'people (in millions)')
#rm(pop_plot_all_countries)

```


These two tables provide us with more insights into the difference between interpolated population and cohort size. 
```{r echo=FALSE}
no_class <- pop_plot_no_country_class %>% 
  filter(population_source == 'diff_population') %>% 
  group_by(population_value) %>% 
  summarise(freq = n()) %>% 
  mutate(Countries = "All", PopulationDifference = population_value, Frequency = freq, Proportion = freq/(nrow(pop_plot_no_country_class)/length(unique(pop_plot_no_country_class$population_source)))) %>% 
  select(-population_value, -freq)
kable(no_class)

all_countries <- pop_plot_all_countries %>% 
  filter(population_source == 'diff_population') %>% 
  group_by(country, population_value) %>% 
  summarise(freq = n()) %>% 
  mutate(Countries = country, PopulationDifference = population_value, Frequency = freq, Proportion = freq/(nrow(pop_plot_no_country_class)/length(unique(pop_plot_no_country_class$population_source))/length(unique(pop_plot_no_country_class$country_name)) )) %>% 
  select(-population_value, -freq, -country)
kable(all_countries)

rm(pop_plot_no_country_class)
rm(pop_plot_all_countries)

```



## Checking patterns of the specific estimates
```{r include=FALSE}
### prepare and merge the datasets
cen_camp_merge <- cen_camp %>% 
  mutate(id = paste0(country, as.character(year), as.character(age))) %>% 
  mutate(cohort_size_camp = cohort_size, cases_camp = cases, deaths_camp = deaths, dalys_camp = dalys) %>% 
  select(id, cohort_size_camp, cases_camp, deaths_camp, dalys_camp)
cen_novax_merge <- cen_novax %>% 
  mutate(id = paste0(country, as.character(year), as.character(age)))
merged = full_join(cen_novax_merge, cen_camp_merge, by = "id")
rm(cen_camp_merge)
rm(cen_novax_merge)

merged <- merged %>% 
  gather(cohort_size_source, cohort_size_value, c(cohort_size, cohort_size_camp)) %>% 
  gather(cases_source, cases_value, c(cases, cases_camp)) %>%
  gather(deaths_source, deaths_value, c(deaths, deaths_camp)) %>%
  gather(dalys_source, dalys_value, c(dalys, dalys_camp)) %>%
  filter((cohort_size_source == 'cohort_size' & 
          cases_source == 'cases' & 
          deaths_source ==  'deaths' & 
          dalys_source == 'dalys' ) | 
          (cohort_size_source == 'cohort_size_camp' & 
          cases_source == 'cases_camp' & 
          deaths_source ==  'deaths_camp' & 
          dalys_source == 'dalys_camp' ) ) %>% 
  mutate(source = case_when(cohort_size_source == 'cohort_size' ~ 'No vaccination',
                            cohort_size_source == 'cohort_size_camp' ~ 'Campaign, Default')) %>% 
  select(-cohort_size_source, -cases_source, -deaths_source, -dalys_source)
  
### combine the countries
merged_no_country_class <- merged %>% 
  group_by(source, year, age) %>% 
  mutate(cohort_size_value = sum(cohort_size_value)) %>% 
  mutate(cases_value = sum(cases_value)) %>%
  mutate(deaths_value = sum(deaths_value)) %>%
  mutate(dalys_value = sum(dalys_value)) %>%
  filter(country == unique(merged$country)[1]) %>%
  select(-country)

### just to look at if vaccine compaign has effects
merged_no_country_class %>% 
  filter(year == 2021 & age == 25)
  
```


This figure shows the aggregated (for all countries) age distribution patterns by outcome.
```{r echo=FALSE, fig.width=10, fig.height=6}
### prepare the dataset and plot
merged_no_country_year <- merged_no_country_class %>% 
  group_by(source, age) %>% 
  mutate(cohort_size_value = sum(cohort_size_value)) %>% 
  mutate(cases_value = sum(cases_value)) %>%
  mutate(deaths_value = sum(deaths_value)) %>%
  mutate(dalys_value = sum(dalys_value)) %>%
  filter(year == unique(merged_no_country_class$year)[1]) %>%
  select(-year) %>% 
  gather(outcome, outcome_values, cases_value:dalys_value)

merged_no_country_year %>% 
  ggplot(aes(x=age, y=outcome_values/1000000)) + 
  geom_bar(stat="identity", fill="skyblue", alpha=1.0) + 
  theme_minimal() +
  facet_grid(outcome~source, scales = 'free') + 
  labs(y='people (in millions)')
rm(merged_no_country_year)

```


This figure shows the global (simulated countries) burden values by decades 2000-2030. 
```{r echo=FALSE, fig.width=10, fig.height=10}
### prepare the dataset and plot
merged_no_country_2030 <- merged_no_country_class %>% 
  filter(year >= 2000 & year <= 2030) %>% 
  mutate(year_class = case_when(year >= 2000 & year <= 2010 ~ '2000 - 2010',
                                year >= 2011 & year <= 2020 ~ '2011 - 2020',
                                year >= 2021 & year <= 2030 ~ '2021 - 2030',)) %>% 
  group_by(source, year_class) %>% 
  mutate(cases = sum(cases_value), dalys = sum(dalys_value), deaths = sum(deaths_value)) %>% 
  filter(age == unique(age)[1] & (year == 2000 | year == 2011 | year == 2021)) %>% 
  select(year_class, source, cases, dalys, deaths) %>% 
  gather(outcome, outcome_values, cases:deaths)

merged_no_country_2030 %>% 
  ggplot(aes(fill=source, y=outcome_values/1000000, x=source)) + 
  geom_bar(position="dodge", stat="identity") + 
  theme_minimal() + 
  facet_grid(outcome~year_class, scales = 'free') + 
  labs(y='people (in millions)')
rm(merged_no_country_2030)

```


This figure shows the global (simulated countries) burden disease values 2000-2100. 
```{r echo=FALSE, fig.width=10, fig.height=10}
### prepare the dataset and plot
merged_no_country_gathered <- merged_no_country_class %>% 
  mutate(cases = cases_value, deaths = deaths_value, dalys = dalys_value) %>% 
  select(year, age, source, cases:dalys) %>% 
  gather(outcome, outcome_values, cases:dalys)

merged_no_country_gathered %>% 
  ggplot(aes(fill = age, y = outcome_values/1000000, x = year)) +
  geom_bar(position="stack", stat="identity") +
  scale_fill_distiller(palette = "RdPu") +
  theme_minimal() +
  facet_grid(outcome~factor(source, levels = c('No vaccination', 'Campaign, Default')), scales = 'free') + 
  labs(x = 'calendar year', y = 'people (in millions)')
rm(merged_no_country_gathered)

```


