---
title: "Diagnostic Report for the Surveillance Project Results"
date: "`r Sys.time()`"
output:
  html_document:
    toc: true
    toc_float: true
params: 
  surveillance_project_directory: "/home/kaiyuezou/VIMC_Model/surveillance_project/gavi_vimc_cholera"
  country: ["GHA", "TZA", "COD"] #country code specified or all the countries will be used for the diagnostic report
  vac_incid_thresholds: ["0.001", "2e-04", "1e-04"]
  no_vaccination_surveillance_scenario: "district-estimate"
  args: 'myarg'
---

```{r setup, include=FALSE, dev="CairoPNG", message=FALSE}
# ## For development only 
# params <- new.env()
# params$surveillance_project_directory <- "/home/kaiyuezou/VIMC_Model/surveillance_project/gavi_vimc_cholera"
# params$country <- c("COD", "GHA", "TZA") #country code specified or all the countries will be used for the diagnostic report
# params$vac_incid_thresholds <- c(2e-04, 1e-04)
# params$no_vaccination_surveillance_scenario <- c("district-estimate")

## Adjust the parameters
vac_incid_thresholds <- as.numeric(params$vac_incid_thresholds)

## Try to set the working directory
setwd(params$surveillance_project_directory)

## The necessary packages 
library(knitr)
knitr::opts_chunk$set(
  cache=FALSE,
  cache.lazy = FALSE,
  echo = FALSE,
  dev="CairoPNG",
  error = FALSE,
  fig.align = "center",
  message = TRUE,
  warning = TRUE
  )
library(dplyr)
library(tidyr)
library(ggplot2)
library(magrittr)
library(purrr)
library(readr)
library(ggplot2)
library(kableExtra)
library(Cairo)
sf::sf_use_s2(FALSE)
# ocvImpact package
if (!require('ocvImpact', character.only = T)) {
  roxygen2::roxygenise("packages/ocvImpact")
  install.packages("packages/ocvImpact", type = "source", repos = NULL)
  library('ocvImpact', character.only = T)
}
# for the development convenience 
roxygen2::roxygenise("packages/ocvImpact")
install.packages("packages/ocvImpact", type = "source", repos = NULL)
library('ocvImpact', character.only = T)

## Other new packages (mainly for "rgeoboundaries")
chooseCRANmirror(ind = 77)

package_list <- c(
  "fasterize", 
  "remotes",
  "rgeoboundaries", 
  "ggrepel"
)

for (package in package_list) {
  if (!require(package = package, character.only = T)) {
    if (package == "rgeoboundaries"){
      try({
        remotes::install_gitlab("dickoa/rgeoboundaries")
        remotes::install_github("wmgeolab/rgeoboundaries")
      })
    }else{
      install.packages(pkgs = package)
      library(package = package, character.only = T)
    }
  }
}

## Figure Caption Numbering
capFigNo = 1
#Function to add the Figure Number
capFig = function(x){
    x = paste0("Figure ",capFigNo,". ",x)
    capFigNo <<- capFigNo + 1
    x
}

```


# Modeling results summary for `r stringr::str_extract(params$country, "[A-Z]{3}")`

# Model Settings 
```{r echo=FALSE}
camp_d <- check_model_setting(countries = params$country, scenario = "campaign-default", surveillance_scenario = "district-estimate", thresholds = params$vac_incid_thresholds)
camp_g <- check_model_setting(countries = params$country, scenario = "campaign-default", surveillance_scenario = "global-estimate", thresholds = params$vac_incid_thresholds)
camp_n <- check_model_setting(countries = params$country, scenario = "campaign-default", surveillance_scenario = "no-estimate", thresholds = params$vac_incid_thresholds)
no_vac <- check_model_setting(countries = params$country, scenario = "no-vaccination", surveillance_scenario = params$no_vaccination_surveillance_scenario, thresholds = params$vac_incid_thresholds)
all_set <- rbind(camp_d, camp_g, camp_n, no_vac) %>% 
  arrange(country) 
all_set %>% 
  kableExtra::kable(col.names = names(all_set)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```

```{r include=FALSE, message=FALSE}
# Check whether the output is available to be read in and used 
for(threshold in params$vac_incid_thresholds){
  camp_d <- check_outputs_availability(countries = params$country, scenario = "campaign-default", surveillance_scenario = "district-estimate", threshold = threshold)
  camp_g <- check_outputs_availability(countries = params$country, scenario = "campaign-default", surveillance_scenario = "global-estimate", threshold = threshold)
  camp_n <- check_outputs_availability(countries = params$country, scenario = "campaign-default", surveillance_scenario = "no-estimate", threshold = threshold)
  no_vac <- check_outputs_availability(countries = params$country, scenario = "no-vaccination", surveillance_scenario = params$no_vaccination_surveillance_scenario, threshold = threshold)
  if(!all(camp_d & camp_g & camp_n & no_vac)){
    unavailable <- c("campaign-district estimate", "campaign-global estimate", "campaign-no estimate", "no vaccination")[c(camp_d, camp_g, camp_n, no_vac)]
    stop(paste0("For threshold ", threshold, ", the following scenario(s) does not have the corresponding model output: ", unavailable))
  }
}

# Make a cache that saves all the tables and some important parameters 
cache <- new.env()

# Function that helps get the names of all files
ocvImpact::get_filenames(cache = cache, surveillance_project_directory = params$surveillance_project_directory, 
    pre_country = params$country, pre_vac_incid_thresholds = params$vac_incid_thresholds, 
    no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)

# Functions that aggregate the output across countries
ocvImpact::combine_output(cache = cache, surveillance_project_directory = params$surveillance_project_directory, 
  output_to_combine = c("target_table", "time_table"), save_final_output = TRUE)

# Decide the height of the figs
fig_height <- 5 * length(params$country)
```



# Case figures {.tabset}
## True case {.tabset}
### True case by year {.tabset}
#### True case by year at threshold 1/1000
```{r true case by year 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("True cases by year")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "true_case", threshold = 1/1000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### True case by year at threshold 1/5000
```{r true case by year 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("True cases by year")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "true_case", threshold = 1/5000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### True case by year at threshold 1/10000
```{r true case by year 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("True cases by year")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "true_case", threshold = 1/10000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### True case by district {.tabset}
#### True case by district at threshold 1/1000
```{r true case by district 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("True cases by district")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "true_case", threshold = 1/1000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### True case by district at threshold 1/5000
```{r true case by district 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("True cases by district")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "true_case", threshold = 1/5000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### True case by district at threshold 1/10000
```{r true case by district 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("True cases by district")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "true_case", threshold = 1/10000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### True case cumulative {.tabset}
#### True case cumulative at threshold 1/1000
```{r true case cumulative 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("True cases cumulative")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "true_case", threshold = 1/1000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### True case cumulative at threshold 1/5000
```{r true case cumulative 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("True cases cumulative")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "true_case", threshold = 1/5000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### True case cumulative at threshold 1/10000
```{r true case cumulative 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("True cases cumulative")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "true_case", threshold = 1/10000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```


## Clinical case {.tabset}
### Clinical case by year {.tabset}
#### Clinical case by year at threshold 1/1000
```{r Clinical case by year 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Clinical case by year")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "clinical_case", threshold = 1/1000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Clinical case by year at threshold 1/5000
```{r Clinical case by year 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Clinical case by year")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "clinical_case", threshold = 1/5000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Clinical case by year at threshold 1/10000
```{r Clinical case by year 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Clinical case by year")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "clinical_case", threshold = 1/10000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Clinical case by district {.tabset}
#### Clinical case by district at threshold 1/1000
```{r Clinical case by district 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Clinical case by district")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "clinical_case", threshold = 1/1000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Clinical case by district at threshold 1/5000
```{r Clinical case by district 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Clinical case by district")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "clinical_case", threshold = 1/5000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Clinical case by district at threshold 1/10000
```{r Clinical case by district 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Clinical case by district")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "clinical_case", threshold = 1/10000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Clinical case cumulative {.tabset}
#### Clinical case cumulative at threshold 1/1000
```{r Clinical case cumulative 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Clinical case cumulative")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "clinical_case", threshold = 1/1000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Clinical case cumulative at threshold 1/5000
```{r Clinical case cumulative 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Clinical case cumulative")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "clinical_case", threshold = 1/5000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Clinical case cumulative at threshold 1/10000
```{r Clinical case cumulative 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Clinical case cumulative")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "clinical_case", threshold = 1/10000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```


## Confirmed case {.tabset}
### Confirmed case by year {.tabset}
#### Confirmed case by year at threshold 1/1000
```{r Confirmed case by year 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Confirmed case by year")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "confirmed_case", threshold = 1/1000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Confirmed case by year at threshold 1/5000
```{r Confirmed case by year 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Confirmed case by year")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "confirmed_case", threshold = 1/5000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Confirmed case by year at threshold 1/10000
```{r Confirmed case by year 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Confirmed case by year")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "confirmed_case", threshold = 1/10000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Confirmed case by district {.tabset}
#### Confirmed case by district at threshold 1/1000
```{r Confirmed case by district 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Confirmed case by district")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "confirmed_case", threshold = 1/1000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Confirmed case by district at threshold 1/5000
```{r Confirmed case by district 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Confirmed case by district")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "confirmed_case", threshold = 1/5000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Confirmed case by district at threshold 1/10000
```{r Confirmed case by district 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Confirmed case by district")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "confirmed_case", threshold = 1/10000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Confirmed case cumulative {.tabset}
#### Confirmed case cumulative at threshold 1/1000
```{r Confirmed case cumulative 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Confirmed case cumulative")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "confirmed_case", threshold = 1/1000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Confirmed case cumulative at threshold 1/5000
```{r Confirmed case cumulative 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Confirmed case cumulative")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "confirmed_case", threshold = 1/5000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Confirmed case cumulative at threshold 1/10000
```{r Confirmed case cumulative 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Confirmed case cumulative")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "confirmed_case", threshold = 1/10000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```



## Averted true case {.tabset}
### Averted true case by year {.tabset}
#### Averted true case by year at threshold 1/1000
```{r Averted true case by year 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted true case by year")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_tr_case", threshold = 1/1000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Averted true case by year at threshold 1/5000
```{r Averted true case by year 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted true case by year")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_tr_case", threshold = 1/5000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Averted true case by year at threshold 1/10000
```{r Averted true case by year 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted true case by year")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_tr_case", threshold = 1/10000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Averted true case by district {.tabset}
#### Averted true case by district at threshold 1/1000
```{r Averted true case by district 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted true case by district")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_tr_case", threshold = 1/1000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Averted true case by district at threshold 1/5000
```{r Averted true case by district 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted true case by district")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_tr_case", threshold = 1/5000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Averted true case by district at threshold 1/10000
```{r Averted true case by district 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted true case by district")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_tr_case", threshold = 1/10000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Averted true case cumulative {.tabset}
#### Averted true case cumulative at threshold 1/1000
```{r Averted true case cumulative 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted true case cumulative")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_tr_case", threshold = 1/1000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Averted true case cumulative at threshold 1/5000
```{r Averted true case cumulative 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted true case cumulative")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_tr_case", threshold = 1/5000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Averted true case cumulative at threshold 1/10000
```{r Averted true case cumulative 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted true case cumulative")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_tr_case", threshold = 1/10000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```


## Averted clinical case {.tabset}
### Averted clinical case by year {.tabset}
#### Averted clinical case by year at threshold 1/1000
```{r Averted clinical case by year 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted clinical case by year")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cl_case", threshold = 1/1000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Averted clinical case by year at threshold 1/5000
```{r Averted clinical case by year 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted clinical case by year")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cl_case", threshold = 1/5000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Averted clinical case by year at threshold 1/10000
```{r Averted clinical case by year 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted clinical case by year")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cl_case", threshold = 1/10000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Averted clinical case by district {.tabset}
#### Averted clinical case by district at threshold 1/1000
```{r Averted clinical case by district 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted clinical case by district")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cl_case", threshold = 1/1000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Averted clinical case by district at threshold 1/5000
```{r Averted clinical case by district 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted clinical case by district")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cl_case", threshold = 1/5000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Averted clinical case by district at threshold 1/10000
```{r Averted clinical case by district 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted clinical case by district")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cl_case", threshold = 1/10000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Averted clinical case cumulative {.tabset}
#### Averted clinical case cumulative at threshold 1/1000
```{r Averted clinical case cumulative 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted clinical case cumulative")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cl_case", threshold = 1/1000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Averted clinical case cumulative at threshold 1/5000
```{r Averted clinical case cumulative 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted clinical case cumulative")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cl_case", threshold = 1/5000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Averted clinical case cumulative at threshold 1/10000
```{r Averted clinical case cumulative 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted clinical case cumulative")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cl_case", threshold = 1/10000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```


## Averted confirmed case {.tabset}
### Averted confirmed case by year {.tabset}
#### Averted confirmed case by year at threshold 1/1000
```{r Averted confirmed case by year 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted confirmed case by year")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cf_case", threshold = 1/1000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Averted confirmed case by year at threshold 1/5000
```{r Averted confirmed case by year 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted confirmed case by year")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cf_case", threshold = 1/5000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Averted confirmed case by year at threshold 1/10000
```{r Averted confirmed case by year 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted confirmed case by year")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cf_case", threshold = 1/10000, cumulative_type = "non_cumulative", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Averted confirmed case by district {.tabset}
#### Averted confirmed case by district at threshold 1/1000
```{r Averted confirmed case by district 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted confirmed case by district")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cf_case", threshold = 1/1000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Averted confirmed case by district at threshold 1/5000
```{r Averted confirmed case by district 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted confirmed case by district")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cf_case", threshold = 1/5000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Averted confirmed case by district at threshold 1/10000
```{r Averted confirmed case by district 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted confirmed case by district")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cf_case", threshold = 1/10000, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Averted confirmed case cumulative {.tabset}
#### Averted confirmed case cumulative at threshold 1/1000
```{r Averted confirmed case cumulative 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted confirmed case cumulative")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cf_case", threshold = 1/1000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Averted confirmed case cumulative at threshold 1/5000
```{r Averted confirmed case cumulative 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted confirmed case cumulative")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cf_case", threshold = 1/5000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Averted confirmed case cumulative at threshold 1/10000
```{r Averted confirmed case cumulative 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Averted confirmed case cumulative")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_cases(cache = cache, case_type = "averted_cf_case", threshold = 1/10000, cumulative_type = "country_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```



# Efficacy figures {.tabset}
## Efficacy side-by-side comparison {.tabset}
### Efficacy side-by-side comparison by year {.tabset}
#### Efficacy side-by-side comparison by year at threshold 1/1000
```{r Efficacy side-by-side comparison by year 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy side-by-side comparison by year")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "side-by-side", threshold = 1/1000, cumulative_type = "non_cumulative")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Efficacy side-by-side comparison by year at threshold 1/5000
```{r Efficacy side-by-side comparison by year 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy side-by-side comparison by year")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "side-by-side", threshold = 1/5000, cumulative_type = "non_cumulative")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Efficacy side-by-side comparison by year at threshold 1/10000
```{r Efficacy side-by-side comparison by year 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy side-by-side comparison by year")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "side-by-side", threshold = 1/10000, cumulative_type = "non_cumulative")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Efficacy side-by-side comparison by district {.tabset}
#### Efficacy side-by-side comparison by district at threshold 1/1000
```{r Efficacy side-by-side comparison by district 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy side-by-side comparison by district")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "side-by-side", threshold = 1/1000, cumulative_type = "within_district")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Efficacy side-by-side comparison by district at threshold 1/5000
```{r Efficacy side-by-side comparison by district 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy side-by-side comparison by district")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "side-by-side", threshold = 1/5000, cumulative_type = "within_district")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Efficacy side-by-side comparison by district at threshold 1/10000
```{r Efficacy side-by-side comparison by district 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy side-by-side comparison by district")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "side-by-side", threshold = 1/10000, cumulative_type = "within_district")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Efficacy side-by-side comparison all-year {.tabset}
#### Efficacy side-by-side comparison all-year at threshold 1/1000
```{r Efficacy side-by-side comparison all-year 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy side-by-side comparison all-year")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "side-by-side", threshold = 1/1000, cumulative_type = "across_year")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Efficacy side-by-side comparison all-year at threshold 1/5000
```{r Efficacy side-by-side comparison all-year 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy side-by-side comparison all-year")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "side-by-side", threshold = 1/5000, cumulative_type = "across_year")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Efficacy side-by-side comparison all-year at threshold 1/10000
```{r Efficacy side-by-side comparison all-year 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy side-by-side comparison all-year")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "side-by-side", threshold = 1/10000, cumulative_type = "across_year")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```


## Efficacy subtraction comparison {.tabset}
### Efficacy subtraction comparison by year {.tabset}
#### Efficacy subtraction comparison by year at threshold 1/1000
```{r Efficacy subtraction comparison by year 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy subtraction comparison by year")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "subtraction", threshold = 1/1000, cumulative_type = "non_cumulative")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Efficacy subtraction comparison by year at threshold 1/5000
```{r Efficacy subtraction comparison by year 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy subtraction comparison by year")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "subtraction", threshold = 1/5000, cumulative_type = "non_cumulative")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Efficacy subtraction comparison by year at threshold 1/10000
```{r Efficacy subtraction comparison by year 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy subtraction comparison by year")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "subtraction", threshold = 1/10000, cumulative_type = "non_cumulative")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Efficacy subtraction comparison by district {.tabset}
#### Efficacy subtraction comparison by district at threshold 1/1000
```{r Efficacy subtraction comparison by district 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy subtraction comparison by district")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "subtraction", threshold = 1/1000, cumulative_type = "within_district")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Efficacy subtraction comparison by district at threshold 1/5000
```{r Efficacy subtraction comparison by district 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy subtraction comparison by district")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "subtraction", threshold = 1/5000, cumulative_type = "within_district")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Efficacy subtraction comparison by district at threshold 1/10000
```{r Efficacy subtraction comparison by district 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy subtraction comparison by district")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "subtraction", threshold = 1/10000, cumulative_type = "within_district")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

### Efficacy subtraction comparison all-year {.tabset}
#### Efficacy subtraction comparison all-year at threshold 1/1000
```{r Efficacy subtraction comparison all-year 1/1000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy subtraction comparison all-year")}
if((1/1000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "subtraction", threshold = 1/1000, cumulative_type = "across_year")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL) #optional, but safer in case another theme is applied later
}
plt

```

#### Efficacy subtraction comparison all-year at threshold 1/5000
```{r Efficacy subtraction comparison all-year 1/5000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy subtraction comparison all-year")}
if((1/5000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "subtraction", threshold = 1/5000, cumulative_type = "across_year")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```

#### Efficacy subtraction comparison all-year at threshold 1/10000
```{r Efficacy subtraction comparison all-year 1/10000, fig.height=fig_height, fig.width=15, fig.cap=capFig("Efficacy subtraction comparison all-year")}
if((1/10000) %in% vac_incid_thresholds){
  plt <- plot_efficacy(cache = cache, compare_type = "subtraction", threshold = 1/10000, cumulative_type = "across_year")
}else{
  plt <- ggplot() +
    theme_void() +
    geom_text(aes(0,0,label='N/A')) +
    xlab(NULL)
}
plt

```



# Dose tables {.tabset}
## Compaign scenario--district estimate {.tabset}
### By year {.tabset}
#### Threshold 1/1000
```{r echo=FALSE}
if((1/1000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "district-estimate", threshold = 1/1000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/5000
```{r echo=FALSE}
if((1/5000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "district-estimate", threshold = 1/5000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/10000
```{r echo=FALSE}
if((1/10000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "district-estimate", threshold = 1/10000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
### By admin {.tabset}
#### Threshold 1/1000
```{r echo=FALSE}
if((1/1000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "district-estimate", threshold = 1/1000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/5000
```{r echo=FALSE}
if((1/5000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "district-estimate", threshold = 1/5000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/10000
```{r echo=FALSE}
if((1/10000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "district-estimate", threshold = 1/10000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```


## Compaign scenario--global estimate {.tabset}
### By year {.tabset}
#### Threshold 1/1000
```{r echo=FALSE}
if((1/1000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "global-estimate", threshold = 1/1000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/5000
```{r echo=FALSE}
if((1/5000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "global-estimate", threshold = 1/5000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/10000
```{r echo=FALSE}
if((1/10000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "global-estimate", threshold = 1/10000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
### By admin {.tabset}
#### Threshold 1/1000
```{r echo=FALSE}
if((1/1000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "global-estimate", threshold = 1/1000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/5000
```{r echo=FALSE}
if((1/5000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "global-estimate", threshold = 1/5000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/10000
```{r echo=FALSE}
if((1/10000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "global-estimate", threshold = 1/10000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```


## Compaign scenario--no estimate {.tabset}
### By year {.tabset}
#### Threshold 1/1000
```{r echo=FALSE}
if((1/1000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "no-estimate", threshold = 1/1000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/5000
```{r echo=FALSE}
if((1/5000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "no-estimate", threshold = 1/5000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/10000
```{r echo=FALSE}
if((1/10000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "no-estimate", threshold = 1/10000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
### By admin {.tabset}
#### Threshold 1/1000
```{r echo=FALSE}
if((1/1000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "no-estimate", threshold = 1/1000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/5000
```{r echo=FALSE}
if((1/5000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "no-estimate", threshold = 1/5000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/10000
```{r echo=FALSE}
if((1/10000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "campaign-default", surveillance_scenario = "no-estimate", threshold = 1/10000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```


## No vaccination scenario {.tabset}
### By year {.tabset}
#### Threshold 1/1000
```{r echo=FALSE}
if((1/1000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "no-vaccination", surveillance_scenario = params$no_vaccination_surveillance_scenario, threshold = 1/1000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/5000
```{r echo=FALSE}
if((1/5000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "no-vaccination", surveillance_scenario = params$no_vaccination_surveillance_scenario, threshold = 1/5000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/10000
```{r echo=FALSE}
if((1/10000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "no-vaccination", surveillance_scenario = params$no_vaccination_surveillance_scenario, threshold = 1/10000)$df_admin1_sumadmins
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
### By admin {.tabset}
#### Threshold 1/1000
```{r echo=FALSE}
if((1/1000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "no-vaccination", surveillance_scenario = params$no_vaccination_surveillance_scenario, threshold = 1/1000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/5000
```{r echo=FALSE}
if((1/5000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "no-vaccination", surveillance_scenario = params$no_vaccination_surveillance_scenario, threshold = 1/5000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```
#### Threshold 1/10000
```{r echo=FALSE}
if((1/10000) %in% vac_incid_thresholds){
  table <- get_inc_tp_doses(countries = params$country, scenario = "no-vaccination", surveillance_scenario = params$no_vaccination_surveillance_scenario, threshold = 1/10000)$df_admin1_byadmin
}else{
  table <- tibble::tibble(ISO = as.character())
}
table %>% 
  kableExtra::kable(col.names = names(table)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(0, bold = T)

```



# Time Table
```{r echo=FALSE}
plot_time_table(cache)

```



```{r eval=FALSE, include=FALSE, message=FALSE}
#Back-ups
# # Function that returns cases plots (case type: true_case, clinical_case, confirmed_case, averted_tr_case, averted_cl_case, averted_cf_case) (cumulative_type: non_cumulative, district_level, country_level)
# plt <- plot_cases(cache = cache, case_type = "true_case", threshold = 0.001, cumulative_type = "district_level", no_vaccination_surveillance_scenario = params$no_vaccination_surveillance_scenario)

# # Function that returns efficacy plots (compare_type: side-by-side, subtraction) (cumulative_type: non_cumulative, across_year, within_district)
# plt <- plot_efficacy(cache = cache, compare_type = "side-by-side", threshold = 0.001, cumulative_type = "non_cumulative")

#The district issue
https://www.datacamp.com/tutorial/facets-ggplot-r 

#To add bar chart 
https://r-graph-gallery.com/line-chart-dual-Y-axis-ggplot2.html 

```
