---
title: "Tradeoff figures (VIMC 2023 resubmission)"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE, 
                      warning=FALSE)

library(reactable)
library(dplyr)
library(tidyr)
library(ggplot2)
library(RColorBrewer)
library(raster)
library(tidyverse)
library(patchwork)
library(countrycode)
library(flextable)
library(cowplot)
#library(GADMTools)
library(magick)
library(ggpubr)
library(wbstats)

source("figures_utils.R")

tab.counter <- 1
fig.counter <- 1
```

```{r load data}
# averted cases
df_tp_eff <- read.csv("data/tp_eff_ac_byISO_medianCI.csv") # by ISO
df_tp_eff_allISOs <- read.csv("data/tp_eff_ac_allISOs_medianCI.csv") # all ISO 

# percent of true averted cases
n_prop_ac_allISOs_medianCI <- read.csv("data/n_prop_ac_allISOs_medianCI.csv") # all ISO
prop_ac_byISO_medianCI <- read.csv("data/prop_ac_byISO_medianCI.csv") # by ISO

# total cost 
cost_allISOs_medianCI <- read.csv("data/cost/cost_allISOs_medianCI.csv") # all ISO
ocv_cost_byISO_medianCI <- read.csv("data/cost/ocv_cost_byISO_medianCI.csv")
test_cost_byISO_medianCI <- read.csv("data/cost/test_cost_byISO_medianCI.csv")

# cost per avert case
total_costeff_allISOs_medianCI <- read.csv("data/cost/total_costeff_allISOs_medianCI.csv")
total_costeff_byISO_medianCI <- read.csv("data/cost/total_costeff_byISO_medianCI.csv")

# read in baseline incidence of each country
df_incid0 <- read.csv("data/df_incid0.csv") %>% dplyr::select(-X)
```


```{r}
# get the total cost (OCV + test) of each ISO
cost_byISO_medianCI <- 
  ocv_cost_byISO_medianCI %>%
  left_join(
    test_cost_byISO_medianCI %>% 
      dplyr::select(ISO, threshold, confirmation_lens, admin_level,
                    test_cost_lb, test_cost_median, test_cost_ub),
    by = c("ISO", "confirmation_lens", "threshold", "admin_level")
  )

cost_byISO_medianCI[is.na(cost_byISO_medianCI)] <- 0
cost_byISO_medianCI <- cost_byISO_medianCI %>%
  mutate(cost_median = ocv_cost_median + test_cost_median) %>%
  dplyr::select(1:4, cost_median)
```

```{r}
# join byISO data together 
df.byISO <- 
  df_tp_eff %>%
  dplyr::select(ISO, threshold, confirmation_lens, admin_level, efficiency_median, ac_median) %>%
  left_join(
    cost_byISO_medianCI, by = c("ISO", "confirmation_lens", "threshold", "admin_level")
  ) %>%
  left_join(
    total_costeff_byISO_medianCI %>% 
      dplyr::select(ISO, threshold, confirmation_lens, admin_level, costeff_ocv_test_median),
    by = c("ISO", "confirmation_lens", "threshold", "admin_level")
  ) %>%
  # filter out those without vaccination going on 
  filter(!is.na(efficiency_median))

# join allISOs data together 
df.allISOs <-
  df_tp_eff_allISOs %>% 
  dplyr::select(-tp_cumu_lb, -tp_cumu_median, -tp_cumu_ub) %>%
  left_join(
    cost_allISOs_medianCI %>%
      dplyr::select(-c(ocv_cost_lb, ocv_cost_median, ocv_cost_ub, test_cost_lb, test_cost_median, test_cost_ub)), by = c("threshold", "confirmation_lens", "admin_level")
  ) %>%
  left_join(
    total_costeff_allISOs_medianCI, by = c("threshold", "confirmation_lens", "admin_level")
  )
  
```

<br>

```{r, echo = T}
baseline_ir_median <- median(df_incid0$baseline_incidence)
median(df_incid0$baseline_incidence)
```

```{r}
# group countries into regions:
# function code from mapping pipeline:
df.byISO <- df.byISO %>% 
    dplyr::mutate(
      AFRO_region = dplyr::case_when(
        ISO %in% c("BDI","ETH","KEN","MDG","RWA","SDN","SSD","UGA","TZA","DJI","SOM","SDN") ~ "Eastern Africa",
        ISO %in% c("MOZ","MWI","NAM","SWZ","ZMB","ZWE","ZAF") ~ "Southern Africa",
        ISO %in% c("AGO","CMR","CAF","TCD","COG","COD","GNQ","GAN") ~ "Middle Africa",
        ISO %in% c("BEN","BFA","CIV","GHA","GIN","GNB","LBR","MLI","MRT","NER","NGA","SEN","SLE","TGO") ~ "Western Africa"))

df.byISO <- df.byISO %>%
  left_join(df_incid0 %>% dplyr::select(ISO, baseline_incidence),
            by = "ISO") %>%
  mutate(burden = ifelse(baseline_incidence > baseline_ir_median, "high", "low"))

high.burden.ISO <- unique((df.byISO %>% filter(burden == "high"))$ISO)
low.burden.ISO <- unique((df.byISO %>% filter(burden == "low"))$ISO)
```
<br>

### By country:

### **Figure `r fig.counter`.**  Total cost ~ total averted cases 
```{r, fig.width = 10, fig.height = 5}
df.byISO %>% 
  filter(admin_level == "admin2") %>%
  filter(confirmation_lens != "global-estimate") %>%
  ggplot() +
  geom_point(aes(x = (ac_median/1000), y = (cost_median/1000000), color = as.factor(confirmation_lens))) +
  facet_grid(. ~ factor(threshold)) +
  scale_x_sqrt() +  scale_y_sqrt() +
  xlab("Total averted cases (K)") +
  ylab("Total cost (million)") +
  labs(color ="Threshold") +
  theme_bw() +
  theme(legend.position = "top") 
```

<br>

### Follow up after the meeting, to see the difference between the high burden 
```{r}
df.byISO %>% 
  filter(admin_level == "admin2") %>%
  filter(confirmation_lens != "global-estimate") %>%
  ggplot() +
  geom_point(aes(x = (ac_median/1000), y = (cost_median/1000000), color = as.factor(confirmation_lens))) +
  facet_grid(burden ~ factor(threshold)) +
  scale_x_sqrt() +  scale_y_sqrt() +
  xlab("Total averted cases (K)") +
  ylab("Total cost (million)") +
  labs(color ="Threshold") +
  theme(legend.position = "top")
```


```{r, fig.width=10, fig.height = 10}
fig.counter <- fig.counter + 1

df.byISO %>% 
  filter(admin_level == "admin2") %>%
  filter(confirmation_lens != "global-estimate") %>%
  ggplot() +
  geom_point(aes(x = (ac_median/1000), y = (cost_median/1000000), color = as.factor(confirmation_lens))) +
  facet_grid(AFRO_region ~ factor(threshold)) +
  scale_x_sqrt() +  scale_y_sqrt() +
  xlab("Total averted cases (K)") +
  ylab("Total cost (million)") +
  labs(color ="Threshold") +
  theme(legend.position = "top")
```

<br>

### **Figure `r fig.counter`.** OCV efficiency ~ cost per averted case
```{r, fig.width =10, fig.height=5}
df.byISO %>% 
  filter(admin_level == "admin2") %>%
  filter(confirmation_lens != "global-estimate") %>%
  filter(ac_median > 1) %>%
  ggplot() +
  geom_point(aes(x = (efficiency_median), y = (costeff_ocv_test_median), color = as.factor(confirmation_lens))) +
  facet_grid(. ~ factor(threshold)) +
  scale_y_log10() +
  xlab("OCV efficiency") +
  ylab("Cost per averted case") +
  labs(color ="Confirmation_lens") +
  theme(legend.position = "top")
```

<br>

### OCV efficiency ~ cost per averted case (by disease burden)
```{r}
df.byISO %>% 
  filter(admin_level == "admin2") %>%
  filter(confirmation_lens != "global-estimate") %>%
  filter(ac_median > 1) %>%
  ggplot() +
  geom_point(aes(x = (efficiency_median), y = (costeff_ocv_test_median), color = as.factor(confirmation_lens))) +
  facet_grid(burden ~ factor(threshold)) +
  scale_y_log10() +
  xlab("OCV efficiency") +
  ylab("Cost per averted case") +
  labs(color ="Confirmation_lens") +
  theme(legend.position = "top")
```

<br>

```{r fig.width=10, fig.height = 7}
fig.counter <- fig.counter + 1

df.byISO %>% 
  filter(admin_level == "admin2") %>%
  filter(confirmation_lens != "global-estimate") %>%
  filter(ac_median > 1) %>%
  ggplot() +
  geom_point(aes(x = (efficiency_median), y = (costeff_ocv_test_median), color = as.factor(confirmation_lens))) +
  facet_grid(AFRO_region ~ factor(threshold)) +
  scale_y_log10() +
  xlab("OCV efficiency") +
  ylab("Cost per averted case") +
  labs(color ="Confirmation_lens") +
  theme(legend.position = "top")
```

<br>

### By scenario (countries aggregated)

### **Figure `r fig.counter`.**  Total cost ~ total averted cases 
```{r fig.width=10, fig.height = 5}
fig.counter <- fig.counter + 1

df.allISOs %>%
  filter(admin_level == "admin2") %>%
  ggplot() +
  geom_point(aes(x = ac_median/1000000, y = total_cost_median/1000000, 
                 color = factor(threshold))) +
  geom_errorbar(aes(x = ac_median/1000000, y = total_cost_median/1000000,
                    xmin = ac_lb/1000000, xmax = ac_ub/1000000, color = factor(threshold)),
                width = 40) +
  geom_errorbar(aes(x = ac_median/1000000, y = total_cost_median/1000000,
                    ymin = total_cost_lb/1000000, ymax = total_cost_ub/1000000, color = factor(threshold)),
                width = 0.02) +
  facet_grid(~ confirmation_lens) +
  xlab("Total averted cases (million)") +
  ylab("Total cost ($million)") +
  labs(color = "Threshold") +
  theme_bw()
```

<br>


### to be put in the extended data file
```{r fig.width=8, fig.height = 8}
# plot all scenarios in one panel
plt.extended5 <-
  df.allISOs %>%
  mutate(confirmation_lens = case_when(confirmation_lens == "district-estimate" ~ "Decentralized Testing",
                                       confirmation_lens == "no-estimate" ~ "Clinical Definition",
                                       confirmation_lens == "global-estimate" ~ "Centralized Testing")) %>%
  mutate(confirmation_lens = factor(confirmation_lens, levels = c("Clinical Definition", "Centralized Testing", "Decentralized Testing"))) %>%
  mutate(threshold = case_when(threshold == 0.001 ~ "10/10,000 per year",
                               threshold == 2e-04 ~ "2/10,000 per year",
                               threshold == 1e-04 ~ "1/10,000 per year")) %>%
  mutate(threshold = factor(threshold, levels = c("10/10,000 per year", "2/10,000 per year", "1/10,000 per year"))) %>%
  filter(admin_level == "admin2") %>%
  ggplot() +
  geom_line(aes(x = ac_median/1000000, y = total_cost_median/1000000, color = confirmation_lens), alpha = 0.45) +

  geom_point(aes(x = ac_median/1000000, y = total_cost_median/1000000, color = confirmation_lens, shape = factor(threshold)), size = 3) +
  geom_errorbar(aes(x = ac_median/1000000, y = total_cost_median/1000000,
                    xmin = ac_lb/1000000, xmax = ac_ub/1000000, color = confirmation_lens), width = 40) +
  geom_errorbar(aes(x = ac_median/1000000, y = total_cost_median/1000000,
                    ymin = total_cost_lb/1000000, ymax = total_cost_ub/1000000, color = confirmation_lens ),
                width = 0.01) +
  xlab("Total averted cases (million)") +
  ylab("Total cost ($million)") +
  labs(color = "Confirmation capacity") + 
  theme_bw() +
  theme(legend.position = "right", legend.box = 'vertical') +
  labs(shape  = "Threshold")

ggsave(plot = plt.extended5, filename = "figures/fig_extended5.jpg", height = 6, width = 8)
```

<br>

### **Figure `r fig.counter`.**  OCV efficiency ~ cost per averted case 
```{r fig.width=10, fig.height = 5}
fig.counter <- fig.counter + 1

df.allISOs %>%
  filter(admin_level == "admin2") %>%
  ggplot() +
  geom_point(aes(x = efficiency_median, y = costeff_ocv_test_median, 
                 color = factor(threshold))) +
  geom_errorbar(aes(x = efficiency_median, y = costeff_ocv_test_median,
                    xmin = efficiency_lb, xmax = efficiency_ub, color = factor(threshold)), width = 0.02) +
  geom_errorbar(aes(x = efficiency_median, y = costeff_ocv_test_median,
                    ymin = costeff_ocv_test_lb, ymax = costeff_ocv_test_ub, color = factor(threshold)),
                width = 0.2) +
  facet_grid(~ confirmation_lens) +
  scale_y_log10() +
  xlab("OCV efficiency") +
  ylab("Cost per averted case") +
  labs(color = "Threshold")
```

<br>

```{r fig.width=8, fig.height = 8}
df.allISOs %>%
  filter(admin_level == "admin2") %>%
  ggplot() +
  geom_point(aes(x = efficiency_median, y = costeff_ocv_test_median, 
                 color = factor(confirmation_lens), shape = factor(threshold)), size = 3) +
  geom_errorbar(aes(x = efficiency_median, y = costeff_ocv_test_median,
                    xmin = efficiency_lb, xmax = efficiency_ub, color = factor(confirmation_lens)), width = 0.02) +
  geom_errorbar(aes(x = efficiency_median, y = costeff_ocv_test_median,
                    ymin = costeff_ocv_test_lb, ymax = costeff_ocv_test_ub, color = factor(confirmation_lens)),
                width = 0.3) +
  geom_line(aes(x = efficiency_median, y = costeff_ocv_test_median, color = confirmation_lens), alpha = 0.45) +
  scale_y_log10() +
  xlab("OCV efficiency") +
  ylab("Cost per averted case") +
  labs(color = "Threshold")
```

<br>

### **Figure `r fig.counter`.**  Total OCV cost ~ total test cost (by baseline burden)
high: higher than baseline median; low: lower than baseline median.
Baseline median: 9.107072e-05.
```{r}
fig.counter <- fig.counter + 1

df.total.cost <- test_cost_byISO_medianCI %>%
  dplyr::select(ISO, confirmation_lens, admin_level, threshold, test_cost_median) %>%
  left_join(
     ocv_cost_byISO_medianCI  %>% dplyr::select(ISO, threshold, confirmation_lens, admin_level, ocv_cost_median)
  ) %>%
  filter(admin_level == "admin2" & confirmation_lens == "district-estimate") %>% 
  filter(ocv_cost_median > 1) %>%
  mutate(burden = ifelse(ISO %in% high.burden.ISO, "high", "low")) %>%
  mutate(test_cost_median = test_cost_median / 1000000,
         ocv_cost_median = ocv_cost_median / 1000000)

df.total.cost %>%
  ggplot() +
  geom_point(aes(x = test_cost_median, y = ocv_cost_median, color = factor(threshold))) +
  scale_x_log10() +
  scale_y_log10() +
  facet_grid(burden ~ .) +
  xlab("Total test cost ($million)") +
  ylab("Total OCV cost ($million)") +
  labs(color = "Threshold")
  

```


